ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-07-07 paper/wish/wsc15paper.tex
final

This paper is organized as follows: In $\mathsection$\ref{IZR}, we recall the
indifference-zone ranking and selection problem. In $\mathsection$\ref{sec:BIZ},
we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\mathsection$\ref{proof},
we present the proof of the validity of the algorithm when the variances
are known. In $\mathsection$\ref{numericalExperiments}, we present some numerical experiments. 
In $\mathsection$\ref{conclusion}, we conclude.

>>>>

This paper is organized as follows: In section \ref{IZR}, we recall the
indifference-zone ranking and selection problem. In section \ref{sec:BIZ},
we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In section \ref{proof},
we present the proof of the validity of the algorithm when the variances
are known. In section \ref{numericalExperiments}, we present some numerical experiments. 
In section \ref{conclusion}, we conclude.
